---
title: "Allelematch 2016"
author: "Coen, Amanda"
date: "March 15, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
library(dynamicTreeCut)
library(allelematch)
```


First, clean up the data from microsat results
1) Sort by samples that are the most complete
2) Replace all 0 values with -99
3) Delete all incomplete samples, add these in as they are completed

Read in the data as a dataframe
```{r, coy_data}

data <- as.data.frame(read.table("data/Coy_Consensus_20170315.txt", header=T, sep="\t")) #needs to be saved as a text file

#need to make sure the empty rows are not showing up as NAs, if so, delete all empty rows

head(data)  #make sure the data was read in properly

#Create a formatted object for analysis with other allematch tools
CoyData_2016 <- amDataset(data, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)

```

Once read in as amDataset, need to find the optimal allele mismatch value 

`amUniqueProfile` Determines optimal parameter values for the identification of unique genotypes

`guessOptimum`  If `TRUE` will guess the optimal value of the parameter being profiled by examining the profile for the first minimum associated with a drop in multiple matches as sensitivity to differences among samples decreases.

`consensusMethod` The method (an integer) used to determine the consensus multilocus genotype from a cluster of multilocus genotypes. See amCluster for details.

```{r, opt_params}

amUniqueProfile(CoyData_2016, guessOptim=T, consensusMethod=1)

```

Current data set shows optimal mismatch is 3

```{r, Coy_output}

Coy_2016_mismatch3 <- amPairwise(CoyData_2016, alleleMismatch = 3)

amCSV.amPairwise(Coy_2016_mismatch3,"data_output/CoyAllelematch_2016_14loci_3miss.csv")

```
Results currently show for 3 mismatch:
F16-062, F16-097, and F16-101 are the same individual
F16-250 and F16-253 are the same individual
F16-314 and F16-316b are the same individual
F16-254b and F16-257 are the same individual
Currently 13 unique individuals

Take these unique individuals and format the data for input into Structure
 - 10000 burn in
 - 100000 MMC
 - 10 Reps
 
Take Results folder, zip it and label with the name of the run, input into structureHarvester
http://taylor0.biology.ucla.edu/structureHarvester/

```{r, gfox_data}

data <- as.data.frame(read.table("data/GFox_Consensus_20170316.txt", header=T, sep="\t")) #needs to be saved as a text file

#need to make sure the empty rows are not showing up as NAs, if so, delete all empty rows

head(data)  #make sure the data was read in properly

#Create a formatted object for analysis with other allematch tools
GFoxData_2016 <- amDataset(data, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)

```

```{r, opt_params_2}

amUniqueProfile(GFoxData_2016, guessOptim=T, consensusMethod=1)

```

Current data set shows optimal mismatch is 3

```{r, GFox_output}

GFox_2016_mismatch3 <- amPairwise(GFoxData_2016, alleleMismatch = 3)

amCSV.amPairwise(GFox_2016_mismatch3,"data_output/GFoxAllelematch_2016_14loci_3miss.csv")

```
Results currently show:
F16-048 and F16-049 are the same individual
F16-063	and F16-115
F16-081	and F16-135
F16-086, F16-087, F16-138 and F16-139
F16-105 and	F16-106
F16-146, F16-148, and F16-151
F16-152	F16-153
F16-166	F16-167
F16-212	F16-215b
F16-227, F16-232, and F16-234
F16-168	F16-165







Currently 15 unique individuals