---
title: "Coyote_SR49"
author: "Coen, Amanda"
date: "March 21, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
library(dynamicTreeCut)
library(allelematch)
library(reshape2)
library(grid)
library(rgdal)  # for vector work; sp package will load with rgdal
library(raster) # for metadata/attributes- vectors or rasters
library(rasterVis)
library(leaflet) # interactive maps
library(viridis) # color palettes
```

First, clean up the data from microsat results
1) Sort by samples that are the most complete
    a) 92% complete   `Coy_Consensus_93_20170322.txt`
    b) 85% complete   `Coy_Consensus_85_20170322.txt`
    c) 77% complete   `Coy_Consensus_77_20170322.txt`
2) Replace all 0 values with -99
3) Delete all incomplete samples, add these in as they are completed
4) Make sure coordinates for Longitude are -121 and -120 (excel likes to remove these symbols)

Read in the data as a dataframe
```{r, coy_data}

data_77 <- as.data.frame(read.table("Projects/NCST/data/Coy/Coy_Consensus_77_20170322.txt", header=T, sep="\t")) #needs to be saved as a text file
data_85 <- as.data.frame(read.table("Projects/NCST/data/Coy/Coy_Consensus_85_20170322.txt", header=T, sep="\t")) #needs to be saved as a text file
data_92 <- as.data.frame(read.table("Projects/NCST/data/Coy/Coy_Consensus_92_20170322.txt", header=T, sep="\t")) #needs to be saved as a text file

#need to make sure the empty rows are not showing up as NAs, if so, delete all empty rows

head(data)  #make sure the data was read in properly

#Create a formatted object for analysis with other allematch tools
CoyData_77_2016 <- amDataset(data_77, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)
CoyData_85_2016 <- amDataset(data_85, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)
CoyData_92_2016 <- amDataset(data_92, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)

```

Once read in as amDataset, need to find the optimal allele mismatch value 

`amUniqueProfile` Determines optimal parameter values for the identification of unique genotypes

`guessOptimum`  If `TRUE` will guess the optimal value of the parameter being profiled by examining the profile for the first minimum associated with a drop in multiple matches as sensitivity to differences among samples decreases.

`consensusMethod` The method (an integer) used to determine the consensus multilocus genotype from a cluster of multilocus genotypes. See amCluster for details.

```{r, opt_params}

amUniqueProfile(CoyData_92_2016, guessOptim=T, consensusMethod=1)  #will guess the optimal value of the parameter being profiled by examining the profile for the first minimum associated with a drop in multiple matches as sensitivity to differences among samples decreases.

```

CoyData_77 shows optimal mismatch is 5 suggests 14 unique
CoyData_85 shows optimal mismatch is 5 suggests 12 unique
CoyData_92 shows optimal mismatch is 5 suggests 9 unique

```{r, goy_output}

Coy77_2016_mismatch4 <- amPairwise(CoyData_77_2016, alleleMismatch = 4)

amCSV.amPairwise(Coy77_2016_mismatch4, "Projects/NCST/data_output/Coy77_Allelematch_14L4M_20170322.csv")

```
Results currently show for 77%: 14 individuals
F16-250 and F16-253 are the same individual
F16-314 and F16-316b are the same individual
F16-254b and F16-257 are the same individual
F16-062, F16-097, and	F16-101 are the same individual

85% 13 individuals (F16-065 is dropped because lower than 85% complete)
F16-250 and F16-253 are the same individual (use `F16-250`)
F16-314 and F16-316b are the same individual (use `F16-316b`)
F16-254b and F16-257 are the same individual (use `F16-254b`)
F16-062, F16-097, and	F16-101 are the same individual (use `F16-062`)
**note** If miscmatch is dropped to 4, F16-097 parses out as unique, no Y marker, missing CPH11 and REN169O18 is 322/328. F16-062 is HO 322, and 101 is HE 322/326 

92% 13 individuals (F16-065, F16-085, F16-103, F16-190, and F16-226 are dropped because lower than 92% complete)
F16-250 and F16-253 are the same individual
F16-314 and F16-316b are the same individual
F16-254b and F16-257 are the same individual
F16-062, F16-097, and	F16-101 are the same individual

Create a csv file cleaning up the Allelematch results, remove K9_AMELO
  - `Coy85_Allelematch_14L4M_20170322.csv` to be used for STRUCTURE Run 
  - compare against `Coy77_Allelematch_14L4M_20170322.csv` results to see which yields a better interpretation

Use csv file in STRUCTURE, zip Results file and import in STRUCTURE Harvester to determine most likely K value

Download Clumpp indfile, use in CLUMPP to generate INDQ files for use in Stacked Bar Plot 

```{r, r_colorsets}
CoyK2_14Lcols <- c("chocolate1", "khaki3", "seashell4")

```

```{r, coy_Runs}
#unsorted
Coy77_K2_14LM4_unsort <- read.table("Projects/NCST/data/Coy77K2_14L4M_unsort.txt", header = TRUE)
Coy77_K3_14LM4_unsort <- read.table("Projects/NCST/data/Coy77K3_14L4M_unsort.txt", header = TRUE)
Coy85_K2_14LM4_unsort <- read.table("Projects/NCST/data/Coy85K2_14L4M_unsort.txt", header = TRUE)

#sorted
Coy77_K2_14LM4 <- read.table("Projects/NCST/data/Coy77K2_14L4M.txt", header = TRUE)
Coy85_K2_14LM4 <- read.table("Projects/NCST/data/Coy85K2_14L4M.txt", header = TRUE)
```

```{r, melt}
#unsorted
Coy77K2_14LM4_unsort.m <- melt(Coy77_K2_14LM4_unsort, id.var="ID")
Coy77K3_14LM4_unsort.m <- melt(Coy77_K3_14LM4_unsort, id.var="ID")
Coy85K2_14LM4_unsort.m <- melt(Coy85_K2_14LM4_unsort, id.var="ID")

#sorted
Coy77K2_14LM4.m <- melt(Coy77_K2_14LM4, id.var="ID")
Coy85K2_14LM4.m <- melt(Coy85_K2_14LM4, id.var="ID")
```

```{r, plot}
Cy77_labs <- factor(Coy77_K2_14LM4$ID, levels = c("F16-207", "F16-190","F16-289",  "F16-205", "F16-085", "F16-065", "F16-142",
                                                  "F16-316b", "F16-254b", "F16-103", "F16-097", "F16-062", "F16-250", "F16-110", "F16-226"))

#x$name <- factor(x$name, levels = x$name[order(x$val)])
#x$name  # notice the changed order of factor levels

Coy77_K2_14LM4$ID <- factor(Coy77_K2_14LM4$ID, levels =Coy77_K2_14LM4$ID[order(Coy77_K2_14LM4$pop1)])
Coy77_K2_14LM4$ID

#Coy85_K2_14LM4$ID <- factor(Coy85_K2_14LM4$ID, levels = unique(Coy85_K2_14LM4$ID)
                            
dev.new()
ggplot(Coy77K2_14LM4.m, 
           aes(x = ID,   #Just sets your x and y values
           y = value, 
           fill = variable, #fill determines groups
           width = 1, # is the width of the bar (from 0 to 1, the latter has no spacing)
           ymax=1.0, 
           ymin=0.0,
           xmax=54,
           xmin=0.0)) +     
  geom_bar(stat = "identity" , colour = "white") + #makes the sep. lines between bars white
  scale_fill_manual(values=CoyK2_14Lcols) +  #Sets the colours (assigned by fill = variable above)
  coord_cartesian(ylim = c(0.1,1)) + #Set your Y limit to be bound 0-1
  ggtitle("Coyote K=2, 77% complete genotype") +
  theme(plot.title = element_text(color="black", size=15, face="bold")) +
  ylab("Probability of assignment\n") + #added newline char to increase space between label
  theme(axis.title.y = element_text(color="black", size=12, face="bold", vjust=0)) + 
  theme(axis.title.x = element_text(color="black", size=12, face="bold")) +
  theme(axis.text.y = element_text(color="black", size=10)) +
  theme(axis.text.x = element_text(face = "italic", angle = 45, vjust=0.9, hjust=1)) + #now labels are in numeric order...grrr
  theme(scale_x_discrete(Cy77_labs)) +
  xlab("Individuals n=15") + # this is where the individual IDs disappear
  #theme(axis.text.x = element_blank()) #+
  #annotation_custom(grob=textGrob("E680",gp=gpar(fontsize=12, col="navyblue")), xmin=3,xmax=3,ymin=-0.05, ymax=-0.05) +
  #theme(axis.ticks.x = element_blank()) #+
  theme(panel.background = element_blank()) +
  #geom_vline(xintercept = c(6.5, 27.5), lwd=0.5, colour="black", lty=1) + #use for creating ticks separating pops
  guides(fill=FALSE)

```

Current image shows a need for sorting individuals
85% image:
  - K1: F16-110, F16-316b, F16-097, F16-205, F16-207, and F16-190
  - K2: F16-062, F16-142, F16-250, F16-289, F16-254b, F16-085, F16-103,
  - K1/K2 (60/40) F16-226

77% K2 image:
  - K1: F16-110, F16-142, F16-205, F16-207, F16-254b and F16-226
  - K2: F16-062, F16-250, F16-289, F16-316b,F16-097, F16-085, F16-103, F16-190, and F16-065
  
77% K3 image:
  - un-true sorting, individuals not entirely assigning to one population or another.
  
#### Mapping

Need to adapt from Class work 

UTM for Study Area = all counties are in Zone 10
 - 

```{r coy_map}

coy <- read.csv("data/Coy/Coy_Microsat_2016_spatial.csv")

# Check how many NA's in spatial data
coy %>% filter(is.na(Lat)) %>% tally # no NAs!

# make the data "spatial":
coy.SP <- SpatialPointsDataFrame(coords = coy[, c("Long", "Lat")], data = coy) #will not work with NAs

# check the CRS
raster::crs(coy.SP) # should be NA
lats <-CRS("+init=epsg:3717") # set the default for lat/longs  4326 = WGS 84 CRS projection EPSG:3717
proj4string(coy.SP) <- lats # assign the CRS we want to use
raster::crs(coy.SP) # should be the full lats obj now

# Transform to UTMs (or whatever)
utms <- CRS("+init=epsg:32610") # zone 10 UTMs

coy_utms.SP<-spTransform(x = coy.SP, CRSobj = utms)

raster::crs(coy_utms.SP) # should be the full UTMs now

# add UTMs as cols to dataframe?
coy.SP@data$utm_y <- coy_utms.SP@coords[,1]
coy.SP@data$utm_x <- coy_utms.SP@coords[,2]

```

```{r, coy_shape}
# shorten/trim all cols to 10 digits
names(coy.SP) <- strtrim(names(coy.SP),10)

writeOGR(coy.SP, dsn="data/GIS", layer="coy",  driver="ESRI Shapefile") # need to correct file path

#### Something is off, this is appearing in the Ocean near the equator!
```

```{r, SR_49}
#read in road shapefile
SR_49 <- readOGR(dsn = ("Projects/NCST/data/GIS"), layer = "tl_2016_06_prisecroads")

# Check what the projection is
crs(SR_49)

```


```{r static plot}
library(maps)
library(mapdata)  
suppressPackageStartupMessages(library(ggmap)) # ggplot functionality for maps
library(ggsn) # for scale bars/north arrows in ggplots

# see what extent is for our shape/points
extent(coy.SP)

# Use this in xlim/ylim
dev.new()

par(mai=c(0.1,0.1,0.1,0.1))
par(pin=c(6,6))
map("state",region=c('CA'), xlim = c(-121.3,-120.65), ylim=c(38.8,39.5))
map.axes()
map("county",region=c('CA'),boundary=FALSE,lty=3, add=TRUE)

#plot highways and highlight 49
plot(SR_49, add = TRUE, lty=1, lwd=1, col= "gray24")
plot(SR_49[SR_49@data$FULLNAME=="State Rte 49",], add=TRUE, lty= 1, lwd=4, col="red")

#add points
plot(coy.SP[coy.SP@data$genotype=="No Genotype",], add = TRUE, pch = 23, bg = "aquamarine2") #not plotting points

#add marker points for those that yeilded a viable genotype for K1 and K2
plot(coy.SP[coy.SP@data$genotype=="K1",], add=TRUE,pch=21, bg="lightslateblue", cex = 1.5) 
plot(coy.SP[coy.SP@data$genotype=="K2",], add=TRUE,pch=21, bg="coral2", cex = 1.5) 


#playing with indicating repeats
plot(coy.SP[coy.SP@data$dlpicate=="1",], add=TRUE,pch=25, bg="forestgreen", cex = 0.8)
plot(coy.SP[coy.SP@data$dlpicate=="2",], add=TRUE,pch=25, bg="blue1", cex = 0.8)
plot(coy.SP[coy.SP@data$dlpicate=="3",], add=TRUE,pch=25, bg="darkslategray", cex = 0.8)

# Create legend
legend("topright", legend = c("Samples collected", "K1 genotype", "K2 genotype"), 
			 pt.bg = c("aquamarine2", "lightslateblue", "coral2"), col = "black",
			 pch = c(23,21,21), cex = c(1.5))

#need to add jitter to stagger the points, choc and khaki are not divergent enough in color for map, need to pick something else
```

##### Pop Gen Analysis

```{r, popgen_libs}

library(pegas)
library(adegenet)
library(PopGenReport)
library(ecodist)
```

#### Frequency Based Statistics

`makefreq` (adegenet) - allele frequency
`allel.rich` (PopGenReport) - allelic richness
`Hs` (adegenet) - Heterozygosity
`Hs.test` (adegenet) - Heterozygosity test
`popgenreport` (PopGenReport) - a whole suite of functions
`HWE.test.genid` (adegenet) - HWE test

```{r, frq_stats}

#read in STRUCTURE file to create a genid object
gfox_obj <- read.structure("Projects/NCST/data/gfox_14L_3M_projdata.stru", 
              n.ind = 64,              # number of individuals
              n.loc = 14,              # number of markers
              onerowperind = TRUE,     # TRUE for single row for individual 
              col.lab = 1,             # integer for column with individual labels
              col.pop = 2,             # integer for column with population assignment
              col.others = 0,          # integer for column with other info (locations?)
              row.marknames = 1   ,    # integer for row containing marker names
              NA.char = "-99", 
              pop = NULL,              # optional factor for population for individuals
              sep = NULL, 
              ask = TRUE, 
              quiet = FALSE)

#create lcoi object for pegas
gfox_pgobj <- genind2loci(gfox_obj)  # may not be needed

#Calculating allele frequency using makefreq from adegenet
gf_freq <- makefreq(gfox_obj, quiet = TRUE, missing = NA, truenames = TRUE)

#Calculating allelic richness from PopGenReport currently says it is not a function
allel.rich(gfox_obj, min.alleles = NULL)  #requires the pop column to be filled

#Calculating Heterozygosity from adegenet
Hs(gfox_obj, pop=NULL) # current heterozygosity is 0.6525153

#Claculating Heterozygosity test  between two groups from adegenet 
Hs.test(gfox_obj, y, n.sim = 999, alter = c("two-sided", "greater", "less")) #alter = string indicating alternative hypothesis

#HWE test from pegas
gf_HWE <- hw.test(gfox_obj, B = 1000)

#Calculating porportion of shared alleles from adegenet
propShared(gfox_obj)

gf_propsh <- genind2df(gfox_obj,sep="|")

# Calculating Linkage Disequilibrium of a matrix from pegas
LDscan(gfox_obj, quiet = TRUE)  #needs to be a phased object in loci object
LDmap(d, POS = NULL, breaks = NULL, col = NULL, border = NA,
angle = 0, asp = 1, cex = 1, scale.legend = 0.8, ...) 


#pairwise.fstb (Popgen)
pairwise.fstb(gfox_obj)  #needs more than one population


#`popgenreport` (PopGenReport) - a whole suite of functions
popgenreport(cats = gfox_obj,                       # genind object
             mk.counts = TRUE,                  # number of individuals, pops, alleles, etc
             mk.map = FALSE,                    # need coordinates if turned on
             maptype = "satellite",             # maps from Google satellite, terrain, hybrid
             mapdotcolor = "blue",              # markers for individuals on map
             mapdotsize = 1,                    # markers for individuals on map 
             mapdotalpha = 0.4,                 # markers for individuals on map
             mapdottype = 19,                   # markers for individuals on map
             mapzoom = NULL,                    # map zoom
             mk.locihz = FALSE,                 # switch for heterozygosity
             mk.hwe = TRUE,                    # switch for HWE
             mk.fst = FALSE,                    # switch for Fst
             mk.gd.smouse = FALSE,              # genetic distance Smouse 1999
             mk.gd.kosman = FALSE,              # genetic distance Kosman 2005
             mk.pcoa = FALSE,                   # PCOA
             mk.spautocor = FALSE,              # Spatial autocorrelation
             mk.allele.dist = FALSE,            # Allelic distribution by loci and subpops
             mk.null.all = FALSE,               # Check for null alleles
             mk.allel.rich = FALSE,             # calculation of allelic richness
             mk.differ.stats = FALSE,           # Looking at population differentiation stats
             mk.custom = FALSE,                 # include cutom function
             fname = "PopGenReport",            # file name
             foldername = "results",            # name where files are stored
             path.pgr = NULL,                   # file path
             mk.Rcode = FALSE,                  # Raw code
             mk.complete = FALSE,               # run all routines
             mk.pdf = TRUE)                     # make a pdf

```


```{r, popgen_plots}

gfplot <- summary(gfox_obj)

names(gfplot)

dev.new()
par(mfrow=c(2,2))
plot(gfplot$loc.n.all, xlab="Sample size", ylab="Number of alleles",main="Alleles numbers and sample sizes", type="n") #not working

text(gfplot$pop.eff,gfplot$pop.nall,lab=names(gfplot$pop.eff))

barplot(gfplot$loc.n.all, ylab="Number of alleles", main="Number of alleles per locus")

barplot(gfplot$Hexp-gfplot$Hobs, main="Heterozygosity: expected-observed", ylab="Hexp - Hobs")

barplot(gfplot$pop.eff, main="Sample sizes per population", ylab="Number of genotypes",las=3)


```

