---
title: "Gray_Fox_SR49"
author: "Coen, Amanda"
date: "March 18, 2017"
output: 
  html_document: 
    fig_height: 10
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
library(dynamicTreeCut)
library(allelematch)
library(reshape2)
library(grid)
library(rgdal)  # for vector work; sp package will load with rgdal
library(raster) # for metadata/attributes- vectors or rasters
library(rasterVis)
library(leaflet) # interactive maps
library(viridis) # color palettes
```

First, clean up the data from microsat results
1) Sort by samples that are the most complete
2) Replace all 0 values with -99
3) Delete all incomplete samples, add these in as they are completed

Read in the data as a dataframe
```{r, gfox_data}

data <- as.data.frame(read.table("Projects/NCST/data/GFox_Consensus_20170316.txt", header=T, sep="\t")) #needs to be saved as a text file

#need to make sure the empty rows are not showing up as NAs, if so, delete all empty rows

head(data)  #make sure the data was read in properly

#Create a formatted object for analysis with other allematch tools
GFoxData_2016 <- amDataset(data, missingCode = "-99", indexColumn = 1, metaDataColumn = NULL)

```

Once read in as amDataset, need to find the optimal allele mismatch value 

`amUniqueProfile` Determines optimal parameter values for the identification of unique genotypes

`guessOptimum`  If `TRUE` will guess the optimal value of the parameter being profiled by examining the profile for the first minimum associated with a drop in multiple matches as sensitivity to differences among samples decreases.

`consensusMethod` The method (an integer) used to determine the consensus multilocus genotype from a cluster of multilocus genotypes. See amCluster for details.

```{r, opt_params}

amUniqueProfile(GFoxData_2016, guessOptim=T, consensusMethod=1)

```

Current data set shows optimal mismatch is 3

```{r, GFox_output}

GFox_2016_mismatch3 <- amPairwise(GFoxData_2016, alleleMismatch = 3)

amCSV.amPairwise(GFox_2016_mismatch3,"data_output/GFoxAllelematch_2016_14loci_3miss.csv")

```
Results currently show:
F16-048 and F16-049 are the same individual
F16-063	and F16-115
F16-081	and F16-135
F16-086, F16-087, F16-138 and F16-139
F16-105 and	F16-106
F16-146, F16-148, and F16-151
F16-152	F16-153
F16-166	F16-167
F16-212	F16-215b
F16-227, F16-232, and F16-234
F16-168	F16-165

Use csv file in STRUCTURE, zip Results file and import in STRUCTURE Harvester to determine most likely K value

Download Clumpp indfile, use in CLUMPP to generate INDQ files for use in Stacked Bar Plot 

```{r, r_colorsets}
GFoxK2_14Lcols <- c("slategray", "wheat3")

```

```{r, GFox_Runs}
GFoxK2_14LM3 <- read.table("Projects/NCST/data/GFox14loc,3missK2.txt", header = TRUE)
GFoxK2_14LM3_unsort <- read.table("Projects/NCST/data/GFox14loc,3missK2_unsorted.txt", header = TRUE)
```

```{r, melt}
GFoxK2_14LM3.m <- melt(GFoxK2_14LM3, id.var="ID")
GFoxK2_14LM3_unsort.m <- melt(GFoxK2_14LM3_unsort, id.var="ID")
```

```{r, plot}
dev.new()
ggplot(GFoxK2_14LM3.m, 
       aes(x = ID,   #Just sets your x and y values
           y = value, 
           fill = variable, #fill determines groups
           width = 1, # is the width of the bar (from 0 to 1, the latter has no spacing)
           ymax=1.0, 
           ymin=0.0,
           xmax=54,
           xmin=0.0)) +     
  geom_bar(stat = "identity" , colour = "white") + #makes the sep. lines between bars white
  scale_fill_manual(values=GFoxK2_14Lcols) +  #Sets the colours (assigned by fill = variable above)
  coord_cartesian(ylim = c(-0.1,1)) + #Set your Y limit to be bound 0-1
  ggtitle("Gray Fox K=2") +
  theme(plot.title = element_text(color="black", size=15, face="bold"))+
  ylab("Probability of assignment\n") + #added newline char to increase space between label
  theme(axis.title.y = element_text(color="black", size=12, face="bold", vjust=0)) + 
  theme(axis.title.x = element_text(color="black", size=12, face="bold")) +
  theme(axis.text.y = element_text(color="black", size=10)) +
  xlab("Individuals n=64") +
  theme(axis.text.x = element_blank()) +
  #annotation_custom(grob=textGrob("E680",gp=gpar(fontsize=12, col="navyblue")), xmin=3,xmax=3,ymin=-0.05, ymax=-0.05) +
  theme(axis.ticks.x = element_blank()) +
  theme(panel.background = element_blank()) +
  #geom_vline(xintercept = c(6.5, 27.5), lwd=0.5, colour="black", lty=1) + #use for creating ticks separating pops
  guides(fill=FALSE)

```

Current image shows a need for sorting individuals
2, 24, 25, 32, 41, 52, 53 all sort to K2 - need to see if this is locationally related
3,7, 38 and 63 have some K2, largely K1

#### Mapping

Need to adapt from Class work 

UTM for Study Area = all counties are in Zone 10
 - 

```{r Gfox_map}

gfox <- read.csv("Projects/NCST/data/GFox_Microsat_ 2016_spatial.csv")

# Check how many NA's in spatial data
gfox %>% filter(is.na(Lat)) %>% tally # no NAs!

# make the data "spatial":
gfox.SP <- SpatialPointsDataFrame(coords = gfox[, c("Long", "Lat")], data = gfox) #will not work with NAs

# check the CRS
raster::crs(gfox.SP) # should be NA
lats <-CRS("+init=epsg:3717") # set the default for lat/longs  4326 = WGS 84 CRS projection EPSG:3717
proj4string(gfox.SP) <- lats # assign the CRS we want to use
raster::crs(gfox.SP) # should be the full lats obj now

# Transform to UTMs (or whatever)
utms <- CRS("+init=epsg:32610") # zone 10 UTMs

gfox_utms.SP<-spTransform(x = gfox.SP, CRSobj = utms)

raster::crs(gfox_utms.SP) # should be the full UTMs now

# add UTMs as cols to dataframe?
gfox.SP@data$utm_y <- gfox_utms.SP@coords[,1]
gfox.SP@data$utm_x <- gfox_utms.SP@coords[,2]

```

```{r, gfox_shape}
# shorten/trim all cols to 10 digits
names(gfox.SP) <- strtrim(names(gfox.SP),10)

writeOGR(gfox.SP, dsn="data/GIS", layer="gfox",  driver="ESRI Shapefile") # need to correct file path

#### Something is off, this is appearing in the Ocean near the equator!
```

```{r, SR_49}
#read in road shapefile
SR_49 <- readOGR(dsn = ("Projects/NCST/data/GIS"), layer = "tl_2016_06_prisecroads")

# Check what the projection is
crs(SR_49)

```


```{r static plot}
library(maps)
library(mapdata)  
suppressPackageStartupMessages(library(ggmap)) # ggplot functionality for maps
library(ggsn) # for scale bars/north arrows in ggplots

# see what extent is for our shape/points
extent(gfox.SP)

# Use this in xlim/ylim
dev.new()
par(mai=c(0.1,0.1,0.1,0.1))
par(pin=c(4,4))
map("state",region=c('CA'), xlim = c(-121.3,-120.65), ylim=c(38.8,39.5))
map.axes()
map("county",region=c('CA'),boundary=FALSE,lty=3, add=TRUE)


plot(SR_49, add = TRUE)

#add points
plot(gfox.SP, add = TRUE, pch = 21, bg = "#FDE725FF") #not plotting points

#add marker points for those that yeilded a viable genotype for K1 and K2
plot(gfox.SP[gfox.SP@data$Genotyped=="K1",], add=TRUE,pch=21, bg="slategray") 
plot(gfox.SP[gfox.SP@data$Genotyped=="K2",], add=TRUE,pch=21, bg= "wheat3") 

# Create legend
legend("topright", legend = c("Samples collected", "K1 genotype", "K2 genotype"), 
			 pt.bg = c("#FDE725FF", "slategray", "wheat3"), col = "black",
			 pch = c(21))

```

##### Pop Gen Analysis

```{r, popgen_libs}

library(pegas)
library(adegenet)
library(PopGenReport)
library(ecodist)
```

#### Frequency Based Statistics

`makefreq` (adegenet) - allele frequency
`allel.rich` (PopGenReport) - allelic richness
`Hs` (adegenet) - Heterozygosity
`Hs.test` (adegenet) - Heterozygosity test
`popgenreport` (PopGenReport) - a whole suite of functions
`HWE.test.genid` (adegenet) - HWE test

```{r, frq_stats}

#read in STRUCTURE file to create a genid object
gfox_obj <- read.structure("Projects/NCST/data/gfox_14L_3M_projdata.stru", 
              n.ind = 64,              # number of individuals
              n.loc = 14,              # number of markers
              onerowperind = TRUE,     # TRUE for single row for individual 
              col.lab = 1,             # integer for column with individual labels
              col.pop = 2,             # integer for column with population assignment
              col.others = 0,          # integer for column with other info (locations?)
              row.marknames = 1   ,    # integer for row containing marker names
              NA.char = "-99", 
              pop = NULL,              # optional factor for population for individuals
              sep = NULL, 
              ask = TRUE, 
              quiet = FALSE)

#create lcoi object for pegas
gfox_pgobj <- genind2loci(gfox_obj)  # may not be needed

#Calculating allele frequency using makefreq from adegenet
gf_freq <- makefreq(gfox_obj, quiet = TRUE, missing = NA, truenames = TRUE)

#Calculating allelic richness from PopGenReport currently says it is not a function
allel.rich(gfox_obj, min.alleles = NULL)  #requires the pop column to be filled

#Calculating Heterozygosity from adegenet
Hs(gfox_obj, pop=NULL) # current heterozygosity is 0.6525153

#Claculating Heterozygosity test  between two groups from adegenet 
Hs.test(gfox_obj, y, n.sim = 999, alter = c("two-sided", "greater", "less")) #alter = string indicating alternative hypothesis

#HWE test from pegas
gf_HWE <- hw.test(gfox_obj, B = 1000)

#Calculating porportion of shared alleles from adegenet
propShared(gfox_obj)

gf_propsh <- genind2df(gfox_obj,sep="|")

# Calculating Linkage Disequilibrium of a matrix from pegas
LDscan(gfox_obj, quiet = TRUE)  #needs to be a phased object in loci object
LDmap(d, POS = NULL, breaks = NULL, col = NULL, border = NA,
angle = 0, asp = 1, cex = 1, scale.legend = 0.8, ...) 


#pairwise.fstb (Popgen)
pairwise.fstb(gfox_obj)  #needs more than one population


#`popgenreport` (PopGenReport) - a whole suite of functions
popgenreport(cats = gfox_obj,                       # genind object
             mk.counts = TRUE,                  # number of individuals, pops, alleles, etc
             mk.map = FALSE,                    # need coordinates if turned on
             maptype = "satellite",             # maps from Google satellite, terrain, hybrid
             mapdotcolor = "blue",              # markers for individuals on map
             mapdotsize = 1,                    # markers for individuals on map 
             mapdotalpha = 0.4,                 # markers for individuals on map
             mapdottype = 19,                   # markers for individuals on map
             mapzoom = NULL,                    # map zoom
             mk.locihz = FALSE,                 # switch for heterozygosity
             mk.hwe = TRUE,                    # switch for HWE
             mk.fst = FALSE,                    # switch for Fst
             mk.gd.smouse = FALSE,              # genetic distance Smouse 1999
             mk.gd.kosman = FALSE,              # genetic distance Kosman 2005
             mk.pcoa = FALSE,                   # PCOA
             mk.spautocor = FALSE,              # Spatial autocorrelation
             mk.allele.dist = FALSE,            # Allelic distribution by loci and subpops
             mk.null.all = FALSE,               # Check for null alleles
             mk.allel.rich = FALSE,             # calculation of allelic richness
             mk.differ.stats = FALSE,           # Looking at population differentiation stats
             mk.custom = FALSE,                 # include cutom function
             fname = "PopGenReport",            # file name
             foldername = "results",            # name where files are stored
             path.pgr = NULL,                   # file path
             mk.Rcode = FALSE,                  # Raw code
             mk.complete = FALSE,               # run all routines
             mk.pdf = TRUE)                     # make a pdf

```


```{r, popgen_plots}

gfplot <- summary(gfox_obj)

names(gfplot)

dev.new()
par(mfrow=c(2,2))
plot(gfplot$loc.n.all, xlab="Sample size", ylab="Number of alleles",main="Alleles numbers and sample sizes", type="n") #not working

text(gfplot$pop.eff,gfplot$pop.nall,lab=names(gfplot$pop.eff))

barplot(gfplot$loc.n.all, ylab="Number of alleles", main="Number of alleles per locus")

barplot(gfplot$Hexp-gfplot$Hobs, main="Heterozygosity: expected-observed", ylab="Hexp - Hobs")

barplot(gfplot$pop.eff, main="Sample sizes per population", ylab="Number of genotypes",las=3)


```

