---
title: "2016_Sampling"
author: "Coen, Amanda"
date: "January 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
library(dplyr)
```

##Sample Progress for extracting, sequencing and genotyping from scat samples collected in 2016


```{r, enter_csv}
scats <- read.csv("data/Sample_Log_2016.csv")

str(scats)

```

If I want to make two dataframes, one for gray fox samples (Gf) and one for coyote (Cy)

```{r, sub_sample}

coys <- scats %>% 
        filter(Sp_fin == "Cy") %>% 
        filter(Re_extract == "") %>% 
        select(Sample, Sp_fin, Sp_call1, Sp_call2)

write.csv(coys, file = "data_output/coy_Msats.csv", row.names=FALSE)

tally(coys)     #currently I have 47 coyote samples (*headdesk*)


gfox <- scats %>% 
        filter(Sp_fin == "Gf") %>% 
        filter(Re_extract == "") %>% 
        select(Sample, Sp_fin, Sp_call1, Sp_call2)

write.csv(gfox, file = "data_output/gfox_Msats.csv", row.names=FALSE)

tally(gfox)    # currently I have 211 gray fox sample (all is not lost)

```

Want to know what samples still need to be re-run 

1)  Failed all 3 pcr tests - need to be re-extracted
2)  Failed first two pcr, successful last...sequence?
3)  Failed two - needs a 3rd pcr  **(pcr_3rd)**
4)  Failed one pcr - needs to be re-run **(pcr_2nd)**
5)  Success 1st time, failed last two - need to be re-extracted
6)  Success 1st and 2nd - need to be sequenced
7)  Success 1st, failed 2nd - need another pcr **(pcr_3rd)**
8)  Success 1st - sequence? (Currently depends on fate of a Ctrl band for this plate)

Samples that need more pcr
```{r, re_pcr}

pcr_3rd <- scats %>% 
           filter(Re_extract == "") %>% # removes any samples that have been re-extracted
           filter(Band_1 == "Yes" | Band_1 == "No") %>% 
           filter(Band_2 == "No") %>% 
           filter(Band_3 == "") %>% 
           filter(Sp_call1 == "Fail" | Sp_call1 == "Human" | Sp_call1 == "") %>% 
           select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1)

pcr_2nd <- scats %>% 
           filter(Re_extract == "") %>% # removes any samples that have been re-extracted
           filter(Band_1 == "No") %>% 
           filter(Band_2 == "") %>% 
           select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1)

#potential_pcr <- scats %>% 
  

# not working, play with later core_columns <- scats %>% select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1)
  
```

Samples ready for sequencing

```{r, seq_ready}

#Samples that failed 1st and 2nd pcr, 3rd gave a band, sequencing still failed, needs to be re-sequenced --or-- Samples that 
seq_FFT <- scats %>% 
           filter(Re_extract == "") %>% # removes any samples that have been re-extracted
           filter(Band_1 == "Yes" | Band_1 == "No") %>% 
           filter(Band_2 == "Yes" | Band_2 == "No") %>% 
           filter(Band_3 == "Yes" | Band_3 == "") %>% 
           filter(Sp_call1 == "Fail" | Sp_call1 == "Human" | Sp_call1 == "") %>% 
           select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1)

```

####Sequencing results

I want to compare success for those samples that were re-sequenced

```{r, reseq_fate}

fail_seq <- scats %>% 
             select(Sample, Sequence_1, Sp_call1, Sequence_2, Sp_call2) %>% 
             filter(Sp_call1 == "Fail") %>% 
             filter(!is.na(Sequence_2))

gf_seq1 <- scats %>% 
           select(Sample, Sequence_1, Sp_call1, Sequence_2, Sp_call2) %>% 
           filter(Sp_call1 == "Gf") %>% 
           filter(Sequence_1 == 20170120) %>% 
           filter(!is.na(Sequence_2))  #yay nothing switched from Gf to other

coy_seq1 <- scats %>% 
           select(Sample, Sequence_1, Sp_call1, Sequence_2, Sp_call2) %>% 
           filter(Sp_call1 == "Cy") %>% 
           filter(Sequence_1 == 20170120) %>% 
           filter(!is.na(Sequence_2))  




```



```{r, re_run_fail_seq}

seq_fail <- scats %>% 
            filter(Sp_call1 == "Fail" | Sp_call1 == "Human") %>% 
            select(Sample, Sp_call1)

tally(seq_fail)   #42 samples that will need to by re-sequenced due to failure (34) or human contamination (8).

summary(seq_fail)
```

```{r, fishy_seqs}
seq_fishy_FB2 <- scats %>% 
              filter(Sp_call1 == "Cy" | Sp_call1 == "Gf") %>% 
              filter(Band_1 == "No") %>% 
              filter(!is.na(Band_2)) %>%
              filter(Band_2 == "No") %>% 
              select (Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, Band_3, Sp_call1)
#Samples 50 (B_1 = F, B_2 = F, Sq = Gf), 114 (B_1 = F, B_2 = F, B_3 = T, Sq = Cy), and 120 (B_1 = F, B_2 = F, B_3 = T, Sq = Gf) all should be re-sequenced using the Band_3 PCR source

seq_fishy_FB1 <- scats %>% 
              filter(Band_1 == "No") %>% 
              filter(is.na(Band_2)) %>%
              select (Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, Band_3, Sp_call1)
#good, no sequences resulted from a sample that failed its only PCR

seq_fishy_F1T2 <- scats %>% 
              filter(Sp_call1 == "Cy" | Sp_call1 == "Gf") %>% 
              filter(Band_1 == "No") %>% 
              filter(!is.na(Band_2)) %>%
              filter(Band_2 == "Yes") %>% 
              select (Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1)
#Samples 106,109,110,142,143,145,148,151,152,153,154. All of these were re-PCR for a 3rd time and will be sent out for sequencing on 01/30/17

```


Next I am sorting by samples that hae failed the first PCR (need to be re-run), passed first but failed a second PCR (Contamination and need to be re-run?), and samples that have failed both PCR runs (need to be re-extracted)

```{r, clutter}

simple_view <- scats %>% 
                filter(Re_extract == "") %>% 
                select(Sample, Band_1, SPID_PCR_1, Band_2, SPID_PCR_2, Band_3, SPID_PCR_3, Sp_call1, Seq_Comp)

```



#Samples that need more PCR work

Only have one Band, which may or may not have failed in sequencing

```{r, pcr2nd}
pcr_2 <- scats %>% 
              filter(Re_extract == "") %>%  #removing  samples that have a secondary extract
              filter(Band_1 == "No") %>%  #Got a band or not first time
              filter(is.na(Band_2)) %>% 
              filter(Sp_call1 == "") %>% 
              select(Sample, Band_1, Band_2, Band_3, Sp_call1)


#not sure below is needed, the only piece that returns is a sample that was later re-extracted
pcr_2seq <- scats %>% 
              filter(Re_extract == "") %>% 
              filter(Band_1 == "No") %>%  #Got a band or not first time
              filter(is.na(Band_2)) %>% 
              filter(Sp_call1 == "Gf" | Sp_call1 == "Cy" | Sp_call1 == "Fail" | Sp_call1 == "Human" ) %>% 
              select(Sample, Band_1, Band_2, Band_3, Sp_call1)

# Use this to find samples that gave a pcr positive the second time and had been sent out for sequencing
pcr_2seqB3_NA <- scats %>% 
               filter(Band_1 == "No") %>% 
               filter(Band_2 == "Yes") %>% 
               filter(is.na(Band_3)) %>% 
               select(Sample, Band_1, SPID_PCR_2, Band_2, Band_3, Sp_call1)

```

Have been attempted twice, need one more attempt

```{r, pcr3rd}

# Use to find samples that require a 3rd pcr attempt
              
pcr_3 <- scats %>% 
              filter(Re_extract == "") %>%  #removes any samples that had been extracted a second time, I don't want to continue working with those older samples
              filter(Band_1 == "No" | Band_1 == "Yes") %>%  #Got a band or not first time
              filter(Band_2 == "No") %>%  # No band on 2nd attempt
              filter(is.na(Band_3)) %>% 
              select(Sample, Band_1, Band_2, Band_3, Sp_call1)

```

####Samples to be sequenced


```{r, seq_20170130}

#sequences needed for those that their 1st pcr was successful
seq_2_pcr1 <- scats %>% 
               filter(Re_extract == "") %>% 
               filter(Band_1 == "Yes") %>% 
               filter(is.na(Band_2)) %>% 
               filter(is.na(Band_3)) %>% 
               select(Sample, SPID_PCR_1, Band_1, Band_2, Band_3, Sp_call1)


#Sequences needed for those that the second pcr was successful
seq_2_pcr2 <- scats %>% 
               filter(Re_extract == "") %>% 
               filter(Band_1 == "No" | Band_1 == "Yes") %>% 
               filter(Band_2 == "Yes") %>% 
               filter(is.na(Band_3)) %>% 
               select(Sample, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3 ,Band_3, Sp_call1)


#Sequences needed for those that 3rd pcr was successful
seq_2_pcr3 <- scats %>% 
               filter(Re_extract == "") %>% 
               filter(Band_1 == "No" | Band_1 == "Yes") %>% 
               filter(Band_2 == "No" | Band_2 == "Yes") %>% 
               filter(!is.na(Band_3)) %>% 
               filter(Band_3 == "Yes") %>% 
               select(Sample, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3 ,Band_3, Sp_call1)

```

Going t filter out samples that have completed the sequencing step( Assigned Gf, Cy, Sk) and have been identified as a species of interest, not failed or Human.

```{r, scat_update}

scats_finished <- scats %>%
                    
                    filter(Seq_Comp == "Yes") %>% 
                    select(Sample, Sp_call1, Seq_Comp)

scats_2bfin1 <- scats %>% 
               filter(Re_extract == "") %>% 
               filter(Sequence_1 == "20170120_Fail" | Sequence_1 == "20170120" | Sequence_1 == "20170130"| Sequence_1 == "") %>% 
               filter(is.na(Seq_Comp)) %>% 
               select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1, Sequence_1, Sequence_2)
#going to need to filter this by Sequence_1 values (20170120, 20170120_Fail, 20170130, ""), and for some Sequence_2 (20170130)  

scats_2bfin2 <- scats %>% 
               filter(Re_extract == "") %>% 
               filter(Sequence_1 == "20170120_Fail" | Sequence_1 == "20170120" | Sequence_1 == "20170130" | Sequence_1 == "") %>% 
               filter(Sequence_2 == "20170130") %>% 
               filter(is.na(Seq_Comp)) %>% 
               select(Sample, SPID_PCR_1, Band_1, SPID_PCR_2, Band_2, SPID_PCR_3, Band_3, Sp_call1, Sequence_1, Sequence_2)
               
                    
```




####Parsing out samples to re-extract after 3 failed PCR attempts 

*(Some of these had a band in the first attempt, but all failed to sequence except as human conatmination)

```{r, re_ex}

re_extract <- scats %>% 
              filter(!is.na(Band_3)) %>% 
              filter(Band_1 == "No" | Band_1 == "Yes") %>%  #Got a band or not first time
              filter(Band_2 == "No") %>%  # No band on 2nd attempt
              filter(Band_3 == "No") %>%  # No band on 3rd attempt
              select(Sample, Band_1, Band_2, Band_3, Sp_call1)   
              
```  


###Sequencing

Samples that need to be sequenced 


```{r, seq_pcr1}

seq_pcr1 <- scats %>% 
            filter(Band_1 == "Yes") %>% 
            filter(is.na(Band_2)) %>% 
            filter(Sp_call1 == "Fail" | Sp_call1 == "Human" | Sp_call1 == "") %>% 
            select(Sample, Band_1, Band_2, Band_3, Sp_call1)


#            filter(Band_3 == "Yes" | Band_2 == "NA") %>%
```



```{r}
#no band on 3rd attempt or have not run a 3rd time

pcr1_fail <- scats %>% 
            filter(Band_1 == "No") %>% 
            filter(is.na(Band_2)) %>% 
            select(Sample, Band_1, Band_2, Sp_call1)   

pcr2_fp <- scats %>% 
           filter(Band_1 == "Yes", Band_2 == "No") %>% 
           select(Sample, Band_1, Band_2, Sp_call1)



```



Saving the current progess as CSV so I can see what samples need to be pulled

```{r, writ_csv}

write.csv(coys, file = "data_output/coy_samples.csv", row.names=FALSE)

write.csv(gfox, file = "data_output/gfox_samples.csv", row.names =FALSE)

#need to see how to combine filtering for multiple....duh | ('or', not , = 'and')

```

Making a list of samples that have been re-extracted to remove from storage and a list for non-target samples to be organized in storage.

```{r, rxted_list}

rxted_list <- scats %>% 
            filter(Re_extract == "Yes") %>% 
            select(Sample, Re_extract)

```

```{r, non_target}

non_target <- scats %>% 
              filter(Re_extract == "") %>%
              filter(Sp_fin == "" | Sp_fin == "Mixed" | Sp_fin == "Miss-Dg" | Sp_fin == "Fail" | Sp_fin == "Miss-Bc" | Sp_fin == "Miss-Mule Deer" | Sp_fin == "Miss-Sk" | Sp_fin == "Miss-Wolf" | Sp_fin == "Miss-Wb" | Sp_fin == "Mixed-Gf") %>% 
              arrange(Sp_fin) %>% 
              select(Sample, Sp_fin)

summary(non_target)

write.csv(non_target, file = "data_output/non_target_Fails.csv", row.names=FALSE)
```


