---
title: "Sierra Nevada Foothill Coyotes"
author: "Coen, Amanda"
date: "December 12, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../"))
knitr::opts_chunk$set(echo = TRUE)
```

```{r,libraries, echo=FALSE, results='hide',message=FALSE}
library(dplyr)
library(sp)
library(rgdal)
library(ggplot2)
library(maps)
library(mapdata) 
library(ggmap)
library(ggsn)
```

This is using file "Sierra_Nevada_Foothill_Coyote_Samples.csv" for samples that were genotyped to 11 loci or greater and checked for duplicated. The file contains: 
+ sample names 
    * (fall of dispersal year
        * F14 is samples collected from Fall 2014 through late summer of 2015)
        * F15 denotes samples collected from spring through summer 2016
+ Latitude
+ Longitude

### Mapping

All counties are in UTM Zone 10

*Read in data*
```{r, coy.coord}

snf.coy <- read.csv("data/Coy/Sierra_Nevada_Foothill_Coyote_Samples.csv", header = TRUE)

summary(snf.coy)

# Check how many NA's in spatial data
snf.coy %>% filter(is.na(Latitude)) %>% tally # no NAs!

# make the data "spatial":
snf.coy.SP <- SpatialPointsDataFrame(coords = snf.coy[, c("Longitude", "Latitude")], data = snf.coy) #will not work with NAs

# check the CRS
raster::crs(snf.coy.SP) # should be NA

# set the default for lat/longs  4326 = WGS 84 CRS projection EPSG:3717
lats <-CRS("+init=epsg:3717") 

# assign the CRS we want to use
proj4string(snf.coy.SP) <- lats 

# should be the full lats obj now
raster::crs(snf.coy.SP) 

# Transform to UTMs (or whatever)
utms <- CRS("+init=epsg:32610") # zone 10 UTMs

snf.coy_utms.SP<-spTransform(x = snf.coy.SP, CRSobj = utms)

raster::crs(snf.coy_utms.SP) # should be the full UTMs now

# add UTMs as cols to dataframe?
snf.coy.SP@data$utm_y <- snf.coy_utms.SP@coords[,1]
snf.coy.SP@data$utm_x <- snf.coy_utms.SP@coords[,2]
```

### Creating the Shapefile

```{r, coy_shape}
# shorten/trim all cols to 10 digits
names(snf.coy.SP) <- strtrim(names(snf.coy.SP),10)

writeOGR(snf.coy.SP, dsn="data/GIS", layer="snf.coy",  driver="ESRI Shapefile") 

#read in road shapefile
SR_49 <- readOGR(dsn = ("data/GIS"), layer = "tl_2016_06_prisecroads")

# Check what the projection is
crs(SR_49) #need to change this from longlat to UTM for zone 10
crs(snf.coy.SP)

#tranforming projection
ca.roads <- spTransform(SR_49, CRS("+init=epsg:3717 +proj=utm +zone=10"))

summary(ca.roads)

#check the projection
crs(ca.roads)

plac.h2o <- readOGR(dsn = ("data/GIS/NEV_PLA_SAC_Water/tl_2017_06057_areawater"), layer ="tl_2017_06057_areawater")
nev.h2o <- readOGR(dsn = ("data/GIS/NEV_PLA_SAC_Water/tl_2017_06061_areawater"), layer ="tl_2017_06061_areawater")
sac.h2o <- readOGR(dsn = ("data/GIS/NEV_PLA_SAC_Water/tl_2017_06067_areawater"), layer ="tl_2017_06067_areawater")
eld.h2o <- readOGR(dsn = ("data/GIS/NEV_PLA_SAC_Water/tl_2017_06017_areawater"), layer ="tl_2017_06017_areawater")
```

### Creating the Map

```{r, coy_map}
# see what extent is for our shape/points
extent(snf.coy.SP)

# Use this in xlim/ylim
dev.new()
par(mai=c(0.1,0.1,0.1,0.1))
par(pin=c(6,6))
map("state",region=c('CA'), xlim = c(-121.4,-120.6), ylim=c(38.29,39.38))
map.axes()
map("county",region=c('CA'),boundary=FALSE,lty=3, lwd=3, add=TRUE)

#plot highways
#plot(ca.roads, add = TRUE, lty=1, lwd=1, col= "blue") # not working, probably be cause of the above transformation

#plotting non-transformed object for speed
plot(SR_49, add=TRUE, lty= 1, lwd=1, col="seashell4")

plot(plac.h2o, add=TRUE, col= "skyblue")
plot(nev.h2o, add=TRUE, col= "skyblue")
plot(sac.h2o, add=TRUE, col= "skyblue")
plot(eld.h2o, add=TRUE, col = "skyblue")

#add points
plot(snf.coy.SP, add = TRUE, pch = 21, col = "black", bg = "magenta1") #not plotting points


# Create legend
#legend("topright", legend = c("Samples collected", "K1 genotype", "K2 genotype"), 
#			 pt.bg = c("aquamarine2", "lightslateblue", "coral2"), col = "black",#
#			 pch = c(23,21,21), cex = c(1.5))

#need to add jitter to stagger the points, choc and khaki are not divergent enough in color for map, need to pick something else
```

